A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-03-01 analysis/paper/paper.Rmd
update paper

<!-- Results  -->
Based on the results of our benchmark, we created a set of practical guidelines for method users `r ref("fig", "user_guidelines")`. The main consideration for the choice of a method is based on the user's existing knowledge about what type of trajectory is expected in the data. If the user expects a linear, cyclic or bifurcating trajectory, a specific set of methods .

>>>>

<!-- Results  -->
Based on the results of our benchmark, we created a set of practical guidelines for method users `r ref("fig", "user_guidelines")`. As method's performance is heavily dependent on the trajectory type being studied, the choice of method will by primarily driven by the prior knowledge of the user about what trajectory topology is expected in the data. For the majority of use cases, the user will know very little about the expected trajectory, except perhaps whether the data is expected to contain multiple trajectories, cycles or a complex tree structure. In each case, a different set of methods performs optimally, with Monocle DDRTree performing best when the data contains a complex tree, while Slingshot performing better when the trajectory could as well be less complex. When the data is expected to contain multiple trajectories or cycles, no methods were included in the current version of the evaluation, although AGA `r cite_methods("aga")` for disconnected trajectories, and Waddington-OT `r cite_methods("wadot")` and AGA `r cite_methods("aga")` for regular graphs are currently the only methods in literature able to handle these types of trajectories. If the user knows the exact topology, our evaluation suggests reCAT for cycles, SCORPIUS for linear trajectories, and slingshot for bifurcating trajectories, although in the last case other topologies could also be returned by the method if it better fits the data. When the users knows the exact . For cases where the user does
